\mytitle

### 2021-12-18 paper.tex
extend text

We define the real dilogarithm $\Li(x)$ for all $x\in\mathbb{R}$ as
the real part of its complex continuation.  The real dilogarithm can
be mapped onto the interval $[0,1/2]$ by using the following
identities \cite{lewin}:
%
\begin{align}
  \Li(x) ={}& \ln(1-x)\left[\frac{1}{2}\ln(1-x) - \ln(-x)\right] - \frac{\pi^2}{6}
              \notag \\ &+\Li\left(\frac{1}{1-x}\right), \quad x\leq -1, \\
  \Li(x) ={}& -\Li\left(\frac{x}{x-1}\right) - \frac{1}{2}\ln^2(1-x),
              \notag \\ & -1<x<0, \\
  \Li(x) ={}& -\Li(1-x) + \frac{\pi^2}{6} - \ln(x) \ln(1-x),
              \notag \\ &\frac{1}{2}<x<1, \\
  \Li(x) ={}& \frac{\pi^2}{6} - \ln(x)\left[\ln\left(1-\frac{1}{x}\right) + \frac{1}{2}\ln(x)\right]
              \notag \\ &+ \Li\left(1-\frac{1}{x}\right), \quad 1<x\leq 2, \\
  \Li(x) ={}& -\Li\left(\frac{1}{x}\right) + \frac{\pi^2}{3} - \frac{1}{2} \ln^2(x), \quad x>2,
\end{align}
%
and by using the special values $\Li(-1)=-\pi^2/12$, $\Li(0)=0$,
$\Li(1/2)=\pi^2/12-\ln^2(2)/2$, $\Li(1)=\pi^2/6$ and $\Li(2)=\pi^2/4$.
Within the interval $[0,1/2]$ the real dilogarithm has the series
expansion \eqref{eq:series}, which can be written as
%
\begin{align}
  \Li(x) = x \sum_{k=0}^\infty \frac{x^{k}}{(k+1)^2}.
  \label{eq:series2}
\end{align}
%
We approximate the sum on the r.h.s.\ of Eq.~\eqref{eq:series2} in the
form of a rational minimax approximant on the interval $[0,1/2]$ using
the \texttt{MiniMaxApproximation} from Wolfram/Mathematica
\cite{mathematica},
%
\begin{align}
  \sum_{k=0}^\infty \frac{x^{k}}{(k+1)^2} \approx
  \frac{\sum_{k=0}^5 p_kx^k}{\sum_{k=0}^6 q_kx^k}.
  \label{eq:minimax}
\end{align}
%
The coefficients $p_k$ and $q_k$ are listed in \tabref{tab:coeffs}.
%
\begin{table}[t]
  \centering
  \caption{Coefficients of the numerator and denominator polynomials
    for the minimax approximant \eqref{eq:minimax}.}
  \begin{tabular}{lr}
    \toprule
    $p_0$ & $ 0.9999999999999999502\cdot 10^{+0}$ \\
    $p_1$ & $-2.6883926818565423430\cdot 10^{+0}$ \\
    $p_2$ & $ 2.6477222699473109692\cdot 10^{+0}$ \\
    $p_3$ & $-1.1538559607887416355\cdot 10^{+0}$ \\
    $p_4$ & $ 2.0886077795020607837\cdot 10^{-1}$ \\
    $p_5$ & $-1.0859777134152463084\cdot 10^{-2}$ \\
    $q_0$ & $ 1.0000000000000000000\cdot 10^{+0}$ \\
    $q_1$ & $-2.9383926818565635485\cdot 10^{+0}$ \\
    $q_2$ & $ 3.2712093293018635389\cdot 10^{+0}$ \\
    $q_3$ & $-1.7076702173954289421\cdot 10^{+0}$ \\
    $q_4$ & $ 4.1596017228400603836\cdot 10^{-1}$ \\
    $q_5$ & $-3.9801343754084482956\cdot 10^{-2}$ \\
    $q_6$ & $ 8.2743668974466659035\cdot 10^{-4}$ \\
    \bottomrule
  \end{tabular}
  \label{tab:coeffs}
\end{table}

>>>>

We define the real dilogarithm $\Li(x)$ for all $x\in\mathbb{R}$ as
the real part of its complex continuation.  The real dilogarithm can
be mapped onto the interval $[0,1/2]$ by using the following
identities \cite{lewin}:
%
\begin{align}
  \Li(x) ={}& \ln(1-x)\left[\frac{1}{2}\ln(1-x) - \ln(-x)\right] - \frac{\pi^2}{6}
              \notag \\ &+\Li\left(\frac{1}{1-x}\right), \quad x\leq -1, \\
  \Li(x) ={}& -\Li\left(\frac{x}{x-1}\right) - \frac{1}{2}\ln^2(1-x),
              \notag \\ & -1<x<0, \\
  \Li(x) ={}& -\Li(1-x) + \frac{\pi^2}{6} - \ln(x) \ln(1-x),
              \notag \\ &\frac{1}{2}<x<1, \\
  \Li(x) ={}& \frac{\pi^2}{6} - \ln(x)\left[\ln\left(1-\frac{1}{x}\right) + \frac{1}{2}\ln(x)\right]
              \notag \\ &+ \Li\left(1-\frac{1}{x}\right), \quad 1<x\leq 2, \\
  \Li(x) ={}& -\Li\left(\frac{1}{x}\right) + \frac{\pi^2}{3} - \frac{1}{2} \ln^2(x), \quad x>2,
\end{align}
%
and by using the special values $\Li(-1)=-\pi^2/12$, $\Li(0)=0$,
$\Li(1/2)=\pi^2/12-\ln^2(2)/2$, $\Li(1)=\pi^2/6$ and $\Li(2)=\pi^2/4$.
Within the interval $[0,1/2]$ the real dilogarithm has the series
expansion \eqref{eq:series}, which can be written as
%
\begin{align}
  \Li(x) = x \sum_{k=0}^\infty \frac{x^{k}}{(k+1)^2}.
  \label{eq:series2}
\end{align}
%
We approximate the sum on the r.h.s.\ of Eq.~\eqref{eq:series2} in the
form of a rational minimax approximant on the interval $[0,1/2]$ using
the \texttt{MiniMaxApproximation} from Wolfram/Mathematica
\cite{mathematica},
%
\begin{align}
  \sum_{k=0}^\infty \frac{x^{k}}{(k+1)^2} \approx
  \frac{\sum_{k=0}^5 p_kx^k}{\sum_{k=0}^6 q_kx^k}.
  \label{eq:minimax}
\end{align}
%
The coefficients $p_k$ and $q_k$ are listed in \tabref{tab:coeffs}.
The approximant on the r.h.s.\ of Eq.~\eqref{eq:minimax} has a maximum
relative error of around $5\cdot 10^{-17}$, suited for an evaluation
of $\Li(x)$ with double precision.
%
\begin{table}[t]
  \centering
  \caption{Coefficients of the numerator and denominator polynomials
    for the minimax approximant \eqref{eq:minimax}.}
  \begin{tabular}{lr}
    \toprule
    $p_0$ & $ 0.9999999999999999502\cdot 10^{+0}$ \\
    $p_1$ & $-2.6883926818565423430\cdot 10^{+0}$ \\
    $p_2$ & $ 2.6477222699473109692\cdot 10^{+0}$ \\
    $p_3$ & $-1.1538559607887416355\cdot 10^{+0}$ \\
    $p_4$ & $ 2.0886077795020607837\cdot 10^{-1}$ \\
    $p_5$ & $-1.0859777134152463084\cdot 10^{-2}$ \\
    $q_0$ & $ 1.0000000000000000000\cdot 10^{+0}$ \\
    $q_1$ & $-2.9383926818565635485\cdot 10^{+0}$ \\
    $q_2$ & $ 3.2712093293018635389\cdot 10^{+0}$ \\
    $q_3$ & $-1.7076702173954289421\cdot 10^{+0}$ \\
    $q_4$ & $ 4.1596017228400603836\cdot 10^{-1}$ \\
    $q_5$ & $-3.9801343754084482956\cdot 10^{-2}$ \\
    $q_6$ & $ 8.2743668974466659035\cdot 10^{-4}$ \\
    \bottomrule
  \end{tabular}
  \label{tab:coeffs}
\end{table}
%
Note that the approximant on the r.h.s.\ of Eq.~\eqref{eq:minimax} is
very similar to the results presented in Ref.~\cite{morris} (DILOG
0011), although with slightly different coefficients.
